\documentclass{article}
\usepackage{graphicx} % Required for inserting images

\title{ENGLISH CLASSES}
\author{Ewerthon Araujo Melzani}
\date{2023}

\begin{document}

\maketitle

\section*{Classe 3}

\vspace*{1.5 cm}

\subsection*{Past Continuous}

I was talking about Israel.

\subsection*{Write a story about a time when you experienced a difficulty and how you overcame it.}

Since I arrived in France, I have had a big problem with the language ,
understanding everything that the people around me were saying. I needed get a certificate
of Level B1 in just one month, which sounded impossible. But to be admitted in ENSTA
I needed this certificate, so I decided to give two hundred percent of myself in
every class. So during this one month, every time that I was having a French course, 
the intensive French class, I was typing and annoting in overleaf all 
the words that the teacher was saying, every single word, and it is funny because
the other guys knew that if they missed any class they could call
me and ask for the class, because I wrote everything that the teacher said.
On the final exam of the course I got B1, but I was certainly aware that my level is under 
this. But , apart from these things, The fact that I was giving all of myself, and
I was always trying to talk with the teachers so they could fix my errors, gave
me an amazing experience, because it was nice time wtih wonderful people, I think
that this is human nature, that we forget, When someone is looking after another
human who is giving his best but still doing poorly, they try to help. It occured
with me, when I was starting at ENSTA, I am still in it, but now I am more conscious,
all the guys were trying to help me, were fixing my errors, were teaching me the 
right words and the right meaning of the expressions.


\vspace*{1.5 cm}


\LARGE{Ewerthon Araujo Melzani}

\vspace*{1.5 cm}

\huge{!SO O GAGA SALVA!}

\end{document}
